% !TeX spellcheck = en_GB
\chapter*{ABSTRACT}
The masters' thesis: \pageref*{MyLastPage}~p., \totfig~fig., \tottab~tabl., \total{citenum}~sources and 3 appendices.

The topic of this masters' thesis is "Stochastic modeling approach to the cars' parking process research".

The object of this thesis is the set of packing and packing processes.

The subject of this thesis is the set of asymptotic properties of several generalizations of R{\'e}nyi parking and packing model.

The purpose of this thesis is the investigation of asymptotic properties of generalized R{\'e}nyi parking and packing model defined by mixture of uniform and determined distributions. 

In this paper the following analytic approaches are used: operational calculus methods, delayed differential equations methods, tauberian theorems. Quadratures are used for numerical integration. Simulations are made based on traditional Monte-Carlo paradigms.

Thesis results:
\begin{itemize}
	\item integral equation for generalized model was built;
	\item was proven that it is possible to apply tauberian theorems in the context of generalized model;
	\item asymptotic equivalence of expectation of saturation level and linear function was shown;
	\item exact, albeit slightly complicated formula for linear function slope was inferred;
	\item the asymptotics were refined using Mellin transform;
	\item was proven that second moment is bounded with linear function;
	\item law of large numbers was proven for saturation level.
\end{itemize}

\MakeUppercase{stochastic process theory, probability theory, delayed differential equation theory, operational calculus, tauberian theorems.}